\subsection{The Different Query Types in ECDAR}
In ECDAR there are currently three different query types for model checking, these three query types are \say{Consistency}, \say{Determinism} and \say{Refinement}. 
These query types can check for certain things on a system, either consisting of one component or a combined component. The combined component can be made with the different operations explained in \autoref{RevaeelOperations}. The three query types will be explained further in the following sections.

\subsubsection*{Consistency} \label{The-Different-Query-Types-In-Ecdar:Consistency}
A consistency query checks whether a system is consistent. 
This means that there are no states in the system that can prevent the system from producing an output, meaning that it is impossible to get stuck in a consistent system.
This also means that systems with an inconsistent state are inconsistent systems \cite{ecdartheory}.


\subsubsection*{Determinism} \label{The-Different-Query-Types-In-Ecdar:Determinism}
A determinism query checks whether a system is deterministic. 
This means that if you are in a specific state in the TIOA and a specific action is performed on the system, the next transition is known and only one possible transition can be made from that \cite{ecdartheory}.


\subsubsection*{Refinement} \label{The-Different-Query-Types-In-Ecdar:Refinement}
A refinement query can match different specifications and replace specifications implemented by components. 
A specification S1 can be replaced by a specification S2, if S2 can satisfy the same system in every environment. 
If it is the case that S2 can replace S1, then it means that S2 refines S1.
A refinement check like this would be formally written as \say{C1 || C2 <= S}, where C1 and C2 are components that the composition operator combines, and S is a specific specification \cite{ecdartheory}.

%A refinement query checks whether composite components match a specification. 
%It does this by looking at the inputs and outputs of the composite components and the specification. 
%It matches and passes the check if and only if every input and output in the composite component is present in the specification.
%But the specification can have other inputs and outputs that the composite component does not have.