\subsection{Committees}
One way collaboration was done was through the use of committees.
This meant that each group had to decide on a representative for each individual committee. These committees were a gRPC committee and a report writing committee.

\subsubsection{gRPC Committee}
The gRPC committee's job was to decide what to include in the protocol.
All work involving the gRPC committee went well, it was well structured, everyone agreed on the structure, and when something had to be changed or added it was done fast and precise.
Whenever someone wanted something added, it was written by that one person and reviewed by the committee.
This meant that only one person at a time worked on the protocol, which led to less confusion and chaos.

\subsubsection{Report Writing Committee}
The report writing committee's job was to decide what to include in the common report part and make sure it was all written.
Some of the problems stated by the different groups about the first report writing part, can be seen below.\\
There was no structure, bad coordination, no leader, the responsibilities were unclear, no one had a complete overview of what was going on, uneven contribution and distribution of work, it was chaotic with the amount of people working in the same document and deadlines weren't met and when writing was stopped it wasn't finished.


The report writing committee was reestablished later on to make the last part of the common report. The last part includes theory, review, retrospective and more.
This went a lot better, it was more structured, more deadlines and they were held. 
It started with a meeting deciding what needs to be added and changed in the report, and dividing that to the different groups so everyone had something to do.
Then another meeting was held making sure everyone had wrote their part, and reviewed what the group, with the group number one higher than themselves, had written.
Assigning reviews like this meant everyone had to review some specific part, and not read the entire report. 
Since there was a lot less to review, and no one besides oneself had to review that part, then people were more motivated to review.
